Upper limits on CN from exocomets transiting $\beta$~Pictoris

### 2025-04-10 src/tex/ms.tex
EdM updates

>>>>

{\bf When creating the CCFs, the region around the narrow, circumstellar \ion{Fe}{I} lines in this wavelength region (see Figs.~\ref{fig:spec_CN_stellar_frame}~and~\ref{fig:spec_CN_comet_frame}) masked to avoid contamination, especially for the higher temperature CN models. We masked the lines detected in \citep{Kiefer2018}, using a width of $\pm$0.35~$\AA$ for the \ion{Fe}{I} 3859.9$\AA$ line, while for the other lines a width of $\pm$0.15$\AA$ was use.}
